Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-27 sections/results.tex
Going through the results section.

\subsubsection{Removal of automatically generated messages}
In Gerrit, the comments are composed of comment messages from reviewers and automated messages. These automatic messages are generated by Gerrit and the integration system to record activities. For example, \textit{'Upload patch set 1.'}, \textit{'Change has been successfully cherry-picked to the staging branch as ...'}. Since these messages are generally recored keeping, they are not substantially relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh} and hence are useless by our definition. In practice they are not considered in code review. They are easily determined as useless by our method and would artificially improve our classification performance. We identified these automatic messages using regular expressions and selecting frequently appeared patterns of messages.

\subsubsection{Data Preprocessing}
 As is customary for VSM processing we extracted semantic words from commit messages and comment messages before converting to vector. For each message, we removed all punctuation signs, digits, and common words (e.g. a, an, the) using Google stop word list\footnote{Available at \url{http://meta.wikimedia.org/wiki/Stop_word_list/google_stop_word_list#English}}. We then used Porter stemming algorithm to remove the commoner morphological and inflexional endings from words in English.

>>>>

\subsubsection{Removal of automatically generated messages}
In Gerrit, the comments are composed of human-written comments from reviewers and automatically generated messages.
These automatic messages are generated by Gerrit, continuous integration system, and the sanity bot\footnote{It is a bot that automatically checks new proposed changes for trivial sanity issues, such as line endings, copyright notices, and commit messages} to record activities.
\textit{`Upload patch set 1.'}, \textit{`Change has been successfully cherry-picked to the staging branch as ...'}, and \textit{`Sanity review passed'} are some examples of these messages.

Since these messages are generally record keeping,
they are not substantially relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh} and hence are useless by our definition.
In practice, they are not considered in code review.
They are easily determined as useless by our method and would artificially improve our classification performance.

These messages are identified by looking for the most common lines of text.
Regular expression patterns are then constructed to match these messages.
Occurrences of these patterns are then removed from our dataset prior to further preprocessing.

Automatic messages are also often inserted as part of review comments.
They too are removed from our dataset, leaving us with only human-written part.
We also completely ignored comments whose author is \emph{Qt Continuous Integration System} and \emph{Qt Sanity Bot}.

\subsubsection{Data preprocessing}
As is customary for VSM processing, we extracted semantic words from commit messages and comment messages before converting to vector.
For each message, we removed all punctuation signs (except apostrophe) and other non alphanumeric characters. We also removed common words (e.g. a, an, the) using Google stop word list\footnote{Available at \url{http://meta.wikimedia.org/wiki/Stop_word_list/google_stop_word_list#English}}. We then used Porter stemming algorithm to remove the commoner morphological and inflexional endings from words in English.
